\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-24 manuscript.Rnw
Use partsurvfit object to create PSM survival models to allow for bootstrapping

@@

psmfit_soc_wei <- flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei)
@

@@

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@

>>>>

One difficulty with partitioned survival analysis is that it does not account for the correlation in the survival endpoints and the curves may consequently cross during the PSA. One way to better account for correlations between the endpoints is to draw PSA samples via bootstrapping whereby the PFS and OS models are refit repeatedly to resamples of the estimation dataset. To allow for bootstrapping we create a \code{partsurvfit} object, which stores both the survival models and the estimation data.

@@

psmfit_soc_wei <- partsurvfit(
  flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
  data = onc_pfs_os
)
@

@@

<<psm_survmods_params>>=
survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
                                 bootstrap = FALSE)
survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
                                         coef_pfs_wei)
survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
                                        coef_os_wei)
survmods_params$pfs$coefs$scale[1:2, ]
@
